Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 nge.tex
Address comments and Notes clean-up

% \subsection{Rationale}
\aanote{I think that the names of the states should be removed. They are
meaningless without the figures. I left them just in case we decide to
reintroduce the figures.}\mtnote{Done.}

@@

\mtnote{NOTE: I would speak about about backfill/not backfill in the discussion
of NGE, when speaking about its generality towards resources, i.e., unified
submission and scheduling process across different resources and multiple
resources. Part of this generality is being able to submit to whatever batch
system is supported by SAGA (including Titan's PBS and all its queues) and, in
case, to multiple resources at the same time.}

\mtnote{NOTE: NGE is not able to use backfill on Titan as we do not have
specific functionalities to interrogate the Moab scheduler about backfill
availability. This is why NGE should be presented as the pilot for PanDA Broker
and not as an alternative to PanDA Broker. Further, NGE alone would not be able
to speak directly to PanDA Server.}

@@

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for communication
and coordination of the execution of units. ORTE is a critical component of the
OpenMPI implementation, developed to support distributed high-performance
computing applications operating in a heterogeneous environment~\cite{castain05:_open_rte, cug-2016}.  
 ORTE transparently provides support for interprocess communication, resource discovery and allocation, and process launching across a variety of platforms. ORTE provides a mechanism similar to the Pilot concept -
it allows the user to create a \emph{``dynamic virtual machine''} (DVM) that
spans multiple nodes. ORTE provides libraries to enable the submission,
monitoring and managing of tasks, avoiding filesystem bottlenecks and race
conditions with network sockets. As a consequence, it is able to minimize the
system overhead while submitting tasks.

>>>>

% \subsection{Rationale}
% \aanote{I think that the names of the states should be removed. They are
% meaningless without the figures. I left them just in case we decide to
% reintroduce the figures.}\mtnote{Done.}

@@

% \mtnote{NOTE: I would speak about about backfill/not backfill in the discussion
% of NGE, when speaking about its generality towards resources, i.e., unified
% submission and scheduling process across different resources and multiple
% resources. Part of this generality is being able to submit to whatever batch
% system is supported by SAGA (including Titan's PBS and all its queues) and, in
% case, to multiple resources at the same time.}
%
% \mtnote{NOTE: NGE is not able to use backfill on Titan as we do not have
% specific functionalities to interrogate the Moab scheduler about backfill
% availability. This is why NGE should be presented as the pilot for PanDA Broker
% and not as an alternative to PanDA Broker. Further, NGE alone would not be able
% to speak directly to PanDA Server.}

@@

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for communication
and coordination of the execution of units. This environment is a critical
component of the OpenMPI implementation, developed to support distributed
high-performance computing applications operating in a heterogeneous
environment~\cite{castain05:_open_rte, cug-2016}.

ORTE provides a mechanism to create a \emph{``dynamic virtual machine''} (DVM)
that spans multiple nodes. The DVM transparently provides support for
interprocess communication, resource discovery and allocation, and process
launching across a variety of platforms. Libraries enable the interaction
between users and ORTE to enable the submission, monitoring and managing of
tasks, avoiding filesystem bottlenecks and race conditions with network sockets.
As a consequence, ORTE is able to minimize the system overhead while submitting
tasks.

% ORTE transparently provides support for interprocess communication, resource
% discovery and allocation, and process launching across a variety of platforms.
% ORTE provides a mechanism similar to the Pilot concept - it allows the user to
% create a \emph{``dynamic virtual machine''} (DVM) that spans multiple nodes.
% ORTE provides libraries to enable the submission, monitoring and managing of
% tasks, avoiding filesystem bottlenecks and race conditions with network sockets.
% \aanote{Requires validation: Alternative version of the three sentences above
% (too many ORTE in my opinion):}
